---
title: "Logistic-Regression"
author: "Varshit Dubey (CoE Pune)"
date: "30 September 2018"
output: github_document
---

# Setup

### Load packages

```{r load-packages, message = FALSE}
library(ggplot2)
library(dplyr)
library(statsr)
library(ggthemes)
library(corrgram)
library(corrplot)
library(caTools)
library(sp)
library(raster)
library(usdm)
library(lmtest)
library(MASS)
library(dplyr)
library(plyr)
library(InformationValue)
library(caret)
 
```

* * *

### Load the data set


```{r}
# load the data set 
library(readxl)
returns1 <- read_excel("returns1.xlsx")
orders <- read_excel("orders.xlsx")

```

```{r}

#View(data)
str(returns1)
returns2 <- returns1[,-c(4:8)]
data1 <- join(orders, returns2, type = "left", by = "Order ID")
#?join
data1$Returned <- ifelse(is.na(data1$Returned),0,1)
sum(is.na(data1$Returned))
any(is.na(data1$Returned))


```

***

## Part 1: Data

The data set is comprised of 9994 observations of sales based on 21 variables.




* * *

## Part 2: Research question



* * *

Now before making the model I am removing some statistically insignificant variables like Product name, Country etc, also I am making a new variable named "days_diff" which is the difference in the shipping date and Order Date and I think that days_diff will have a role to play in the model. 

```{r}
#data$Returned <- factor(data$Returned)

data1$days_diff <- as.Date(data1$`Ship Date`, format="%Y/%m/%d")-
                  as.Date(data1$`Order Date`, format="%Y/%m/%d")


# removing some variables..
data2 <- data1[,-c(2,3,4,6,7,9,10,11,14,17,23,24)]


str(data2)
data2$days_diff <- as.numeric(data2$days_diff)

set.seed(123)
train=createDataPartition(data2$Returned, p=0.7,list=FALSE)

Training=data2[train,]
Testing=data2[-train,]


sum(Training$Returned)
sum(Testing$Returned)
all <- glm(Returned ~.,data = Training, family = binomial(link = "logit"))
summary(all)
a <- stepAIC(all, direction = "both")
summary(a)

vif(data2[,c(1,7:12)])

predicted <- predict(a, newdata = Testing, type="response")

# this will show what should be the optimum cutoff for 0 and 1..
optCutOff <- optimalCutoff(Testing$Returned, predicted)[1]
misClassError(Testing$Returned, predicted, threshold = optCutOff)

plotROC(actuals=Training$Returned,predictedScores=as.numeric(fitted(a)))
Pred2=ifelse(predicted<optCutOff,0,1)


caret::confusionMatrix(table(Testing$Returned,Pred2,dnn=list('actual','predicted')))
```



